### 2019-10-10 paper/introduction.tex
After Osama's comments

\section{Introduction}
The \gls{GIF} has defined eight technology goals for the next generation 
nuclear systems. These goals are: safety and reliability, economics, 
sustainability, non-proliferation and physical protection 
\cite{doe2002technology}. The \gls{MSR} has many advantages that consistent 
with \gls{GIF}'s goals, for example, liquid fuel, inherent safety, online 
reprocessing and refueling, excellent neutron economy and near atmospheric 
pressure in a primary loop \cite{siemer2015molten,rosenthal1970molten}. 
Thus, the \gls{GIF} selected \gls{MSR} as one of the promising Generation-IV 
reactors \cite{doe2002technology,pioro2016handbook}.
In the \gls{MSR}, the fuel is dissolved in a molten salt (e.g., LiF or NaCl). 
This liquid fuel salt (e.g., LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$) constantly 
circulates through the core and allows transferring fission heat from reactor 
core to heat exchanger.

@@

Betzler \emph{et al.} discussed the simulation of the startup of a MSBR unit 
cell with \gls{LEU} (19.79\%) and Pu from \gls{LWR} spent fuel (SF) as initial 
fissile materials \cite{betzler2016modeling}. They concluded that the 
plutonium vector extracted from LWR SF is the best alternative source 
to $^{233}$U because it has the highest ratio of fissile isotopes 
\cite{betzler2016modeling}. Zou \emph{et al.} introduced two approaches for 
the thorium fuel cycle transition in \gls{TMSR}: in-core transition and 
ex-core transition. Historically, the TMSR is launched with existing fissile 
material and thorium as a fertile material; then the $^{233}$U bred from 
thorium is rerouted into the core to maintain criticality. In contrast, the 
new approaches tends to store produced $^{233}$U out of the core until there 
is enough amount to start a new TMSR \cite{zou2018transition}.
Additionally, Zou \emph{et al.} studied the transitioning to thorium fuel 
cycle in a small modular Th-based molten salt reactor (smTMSR) using \gls{TRU} 
as startup fuel. They concluded that the transition to thorium fuel cycle can 
be achieved in thermal smTMSR with a proper fuel fraction 
\cite{zou2018preliminary}.
Heuer \emph{et al.} discussed the transition characteristics of the \gls{MSFR} 
under different launching scenarios (e.g., enriched uranium and TRU) 
\cite{heuer2014towards}.

>>>>

\section{Introduction}
The \gls{GIF} has defined eight technology goals for the next generation
nuclear systems. These goals are: safety and reliability, economics,
sustainability, non-proliferation and physical protection
\cite{doe2002technology}. The \gls{MSR} has many advantages that consistent
with \gls{GIF}'s goals, for example, liquid fuel, inherent safety, online
reprocessing and refueling, excellent neutron economy and operation near
atmospheric
pressure in a primary loop \cite{siemer2015molten,rosenthal1970molten}.
Thus, the \gls{GIF} selected \gls{MSR} as one of the promising Generation-IV
reactors \cite{doe2002technology,pioro2016handbook}.
In the \gls{MSR}, the fuel is dissolved in a molten salt (e.g., LiF or NaCl).
This liquid fuel salt (e.g., LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$) constantly
circulates through the core and allows transferring fission heat from reactor
core to heat exchanger.

@@

Betzler \emph{et al.} discussed the simulation of the startup of a MSBR unit
cell with \gls{LEU} (19.79\%) and Pu from \gls{LWR} spent fuel (SF) as initial
fissile materials \cite{betzler2016modeling}. They concluded that the 
plutonium vector extracted from LWR SF is the best alternative source to 
$^{233}$U because it has the highest ratio of fissile isotopes
\cite{betzler2016modeling}. Zou \emph{et al.} introduced two approaches for
the thorium fuel cycle transition in \gls{TMSR}: (1) in-core transition and 
(2) ex-core transition. In the first approach, the TMSR is launched with 
existing fissile material and thorium as a fertile material; then the 
$^{233}$U bred from thorium is rerouted into the core to maintain criticality. 
In contrast, the second approache tends to store produced $^{233}$U out of the 
core until there is enough amount to start a new TMSR \cite{zou2018transition}.
Additionally, Zou \emph{et al.} studied the transitioning to thorium fuel
cycle in a small modular Th-based molten salt reactor (smTMSR) using \gls{TRU}
as startup fuel. They concluded that the transition to thorium fuel cycle can
be achieved in thermal smTMSR with a proper fuel fraction 
\cite{zou2018preliminary}.

Heuer \emph{et al.} discussed the transition characteristics of the \gls{MSFR}
under different launching scenarios (e.g., enriched uranium and TRU)
\cite{heuer2014towards}.
